\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
\usepackage{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{
\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{
  \end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Aly Chace} \\
  \small 470-512-1448 $|$
  \href{mailto:aly.chace@atolls.com}{aly.chace@atolls.com} $|$
  \href{https://linkedin.com/in/alyraffauf}{linkedin.com/in/alyraffauf} $|$
  \href{https://github.com/alyraffauf}{github.com/alyraffauf}
\end{center}

\section{Summary}
Atlanta-based fanatic for cloud infrastructure, Linux system
administration, and automation using Ansible, AWS, Nix, Docker, and
Python. Recently shifted focus to managing hybrid cloud environments,
building skills in software deployment, CI/CD, data analysis, and
best DevOps practices.

\section{Experience}
\resumeSubHeadingList
\resumeSubheading
{Atolls}{Atlanta, GA}
{Editor}{Aug 2025 -- Present}
\resumeSubheading
{}{}
{Junior Editor}{Aug 2022 -- July 2025}
\resumeSubHeadingList
\resumeItem{\textbullet\ Implemented and developed AI workflows for content creation, review, and optimization.}
\resumeItem{\textbullet\ Contributed to office-wide prompts and best practices materials and discussions for effectively reorienting Coupons.com to a savings and customer-focused destination.}
\resumeItem{\textbullet\ Worked extensively with popular models from Anthropic, Google, and OpenAI, as well as leading open source models (Gemma, Llama, Mistral).}
\resumeItem{\textbullet\ Developed automated ranking/prioritization tool in Python to support editor page prioritization and optimization workflows.}
\resumeItem{\textbullet\ Implemented content strategies for 200+
landing pages on white label \& in-house domains.}
\resumeSubHeadingListEnd
\resumeSubheading
{Georgia State University}{Atlanta, GA}
{Graduate Research Assistant}{Aug 2017 -- Dec 2020}
\resumeSubHeadingList
\resumeItem{\textbullet\ Developed cloud applications in Python for
archiving and processing social media content for a research database.}
\resumeItem{\textbullet\ Performed sentiment analysis with Python's Natural Language Toolkit on large social media corpora.}
\resumeItem{\textbullet\ Worked on the Global Health Discourses
Project, developing visualizations of social network data based on health NGOs.}
\resumeSubHeadingListEnd
\resumeSubheading
{SimpleShowing, Inc.}{Atlanta, GA}
{Intern}{July 2017 -- December 2017}
\resumeSubHeadingList
\resumeItem{\textbullet\ Developed and deployed React.js apps to
Google Cloud Platform.}
\resumeItem{\textbullet\ Developed webscraper in Python to
automatically build a CRM based on real estate listings.}
\resumeItem{\textbullet\ Built an automated SMS-based marketing
outreach tool in Python and deployed to GCP.}
\resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingList
\resumeSubheading
{\href{https://github.com/alyraffauf/nynx}{nynx}}{May 2025 -- Present}
{Flake-Native Deployments for NixOS + macOS}{Golang, Nix, CI/CD}
\resumeSubHeadingList
\resumeItem{\textbullet\ Built a Nix deployment tool in Golang for automatic,
safe, and reproducible deployments to distributed NixOS \& macOS clusters.}
\resumeItem{\textbullet\ Implemented robust CI pipelines to enhance
code integrity and ensure cross-platform reproducibility.}
\resumeSubHeadingListEnd
\resumeSubheading
{\href{https://cute.haus}{cute.haus}}{May 2023 -- Present}
{Hybrid Cloud Homelab}{AWS, Infrastructure as Code, CI/CD}
\resumeSubHeadingList
\resumeItem{\textbullet\ Assembled an 8-node hybrid
  cloud (4 on-prem, 4 on major hosting providers) using declarative Nix
flake deployments.}
\resumeItem{\textbullet\ Deployed LLM-powered applications and chat frontends, including Karakeep and Open WebUI, powered by self-hosted inference APIs (Ollama, Llama.cpp).}
\resumeItem{\textbullet\ Built CI/CD pipelines with
self-hosted runners on Docker, cutting manual deployments from >30min to <5min.}
\resumeItem{\textbullet\ Established site‑to‑site WireGuard and
private DNS, enabling seamless service discovery across VPC and LAN.}
\resumeItem{\textbullet\ Integrated Grafana + Loki + Prometheus, Uptime
Kuma, and Cloudwatch, achieving $>$99\% uptime for 15+ apps.}
\resumeSubHeadingListEnd
\resumeSubheading
{\href{https://github.com/NixOS/nixpkgs}{nixpkgs}}{Feb 2024 -- Present}
{Software Package Repository}{Linux, DevOps}
\resumeSubHeadingList
\resumeItem{\textbullet\ Squashed bugs, troubleshot build errors, and
packaged software in the world's largest Linux + MacOS software repo.}
\resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeSubHeadingList
\resumeItem{\textbf{Cloud Platforms}: AWS (EC2, S3, VPC, IAM,
CloudFormation, Route 53), Google Cloud (Compute Engine, Cloud Storage)}
\resumeItem{\textbf{Infrastructure as Code \& Automation}: Nix
(flakes), Ansible, GitOps, CI/CD Pipelines (GitHub Actions)}
\resumeItem{\textbf{Languages \& Scripting}: Python, Bash, Nix, Golang}
\resumeItem{\textbf{Research}: Ethnography, Data Analysis, Visualization}
\resumeSubHeadingListEnd

% \section{Certifications}
% \resumeSubHeadingList
%   \resumeItem{\textbullet\ Amazon Web Services - Cloud Practitioner}
%   \resumeItem{\textbullet\ Linux Professional Institute - Linux Essentials}
% \resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList
\resumeSubheading
{Georgia State University}{Atlanta, GA}
{M.A. in Anthropology}{Aug 2017 -- May 2019}
\resumeSubheading
{}{}
{B.A. in Applied Linguistics}{Aug 2013 -- May 2017}
\resumeSubHeadingListEnd

\end{document}
